\documentclass{sig-alternate}
\usepackage{subfigure,url} 

\begin{document}

\title{}

\numberofauthors{1}


\author{
\alignauthor
Shava Smallen, Sameer Tilak, etc. \\
\affaddr{University of California, San Diego} \\ 
\affaddr{9500 Gilman Drive, La Jolla, CA 92093-0505, USA}\\ 
\email{\{ssmallen,sameer\}@sdsc.edu}\\
}

\maketitle

\begin{abstract}

\end{abstract}

\section{Introduction}

\section{Future Grid Overview}

The FutureGrid Project provides a geographically distributed experimental platform for computer scientists to understand the behavior and utility of cloud computing approaches. The platform will allow these computer scientists to tackle complex research challenges in the areas ranging from authentication, authorization, scheduling, virtualization, middleware design, interface design and cybersecurity to the optimization of grid-enabled and cloud-enabled computational schemes for researchers in astronomy, chemistry, biology, engineering, atmospheric science and epidemiology. The FutureGrid is a key component of NSF's high-performance cyberinfrastructure and supports innovative computer science research requiring access to lower levels of the grid software stack, the networking software stack, and to virtualization and workflow orchestration tools.

\section{Inca Architecture}

\section{Use cases}

\section{Test suite classes}

\section{Experimental results}

\subsection{Monitoring tools comparison:} Ganglia vs Inca

\subsection{reliability}

\subsection{resource-level}: How do different resources (storage, compute, network) compare in terms of reliability. Where is the bottleneck?
\subsection{sw-stack-level}: How do different layers of the s/w stack compare? Where do failures occur the most? Middleware, Apps, OS, etc....
\subsection{site-level}: How do different sites compare in terms of reliability.
\subsection{software-level:} Should we upgrade? History shows newer releases make the system more stable or less stable.
\subsection{cloud-stats}
\subsection{hpc-stats:} benchmarks, version numbers.
\subsection{Failures distribution:} Are failures independent or related?
\subsection{upgrade stats:} Patches done every month. 
\subsection{predictability} Is this system system predictable in terms of resource availability or failures.
\subsection{Test success rate}


\section{Future Work}

\section{Conclusion}


\bibliographystyle{abbrv}
\bibliography{wsn-dc}

 \end{document}
